---
title: "02-Webscrape_Ki_route_db"
author: "Valentin Marteau"
params:
  data: "../data"
  results:  "../results"
  lib:  "../lib"
  maxcores: 6
output:
  html_notebook:
    theme: spacelab
    highlight: textmate
    toc: yes
    number_sections: true
    toc_depth: 3
    toc_float: true
---

# Set up Selenium using Docker
Need to download and set up a [Docker Selenium image](https://github.com/SeleniumHQ/docker-selenium), start the docker deamon and run:
```{bash, engine.opts='-l'}
# For example:
docker run -d -p 4444:4444 --shm-size="2g" selenium/standalone-firefox:4.1.4-20220427 # If port 4444 is not available try 4445 (can happen on macos)
# Check if image is running
docker ps
# To stop docker
#docker kill "CONTAINER ID"
```
```{r, results = "hide"}
# Load required packages
library(RSelenium)
library(rvest)
library(tidyverse)
```
# Access selenium browser using RSelenium
Need to use the same port as specified in the docker image!
```{r}
remDr <- RSelenium::remoteDriver(remoteServerAddr = "localhost",
                                 port = 4444L,
                                 browserName = "firefox")
# Connect to the server
remDr$open()

# Navigate to url of interest
remDr$navigate("https://www.kletterzentrum-innsbruck.at/index.php?id=235&no_cache=1")
# remDr$screenshot(display = TRUE) #This will take a screenshot and display it in the RStudio viewer

# Define worker function
scrape_table <- function(html){
  read_html(html) |>
  html_table(fill = T) |>
  pluck(3)
}

# Iterate over table content, applying the function each time and clicking the "Next" button
df <- tibble()

for(i in 1:11) {
  df_sub <- scrape_table(remDr$getPageSource()[[1]])
  remDr$findElement('xpath', '//*[@id="climbingRoutes_next"]')$sendKeysToElement(list(key="enter"))
  Sys.sleep(1)
  df <- bind_rows(df, df_sub)
}

write_csv(df, file = file.path(params$results, paste0(lubridate::today(), "-KI_Routendatenbank.csv") ))
```

# References and code snippets for later use
As it took some time to work this out, below you will find a loose collection of hopefully helpfull references and code snippets.

Given the time I would also like to improve the above code to include a while statement (right now I had to manually set the pagination number to 11 but this will probably change!; See https://stackoverflow.com/questions/57657829/how-to-extract-the-inherent-links-from-the-webpage-with-my-code-error-subscrip, https://stackoverflow.com/questions/40366291/how-to-check-if-an-element-is-present-in-the-webpage-using-rselenium). In addition, I am sure there is a better way to loop over the "refreshed" pages (e.g. https://community.rstudio.com/t/scraping-multiple-web-pages-with-rvest-and-for-loop/89661)
I would like to scrape the colours.

The [official vignettes](https://cran.r-project.org/web/packages/RSelenium/index.html) is also really helpful!

Some other example code: https://tagmerge.com/question/r-how-to-web-scrap-data-from-stocktwits-with-rselenium
https://callumgwtaylor.github.io/post/using-rselenium-and-docker-to-webscrape-in-r-using-the-who-snake-database/
http://joshuamccrain.com/tutorials/web_scraping_R_selenium.html

```{r}
# Usefull code to find stuff using xpath (https://tutorialmeta.com/question/error-using-findelement-function-in-rselenium-struggling-to-select-a-text-box-a, https://www.w3schools.com/xml/xpath_syntax.asp)
remDr$navigate("https://trakcarelabwebview.nhls.ac.za/trakcarelab/csp/system.Home.cls#/Component/SSUser.Logon")

remDr$findElement('xpath', '//*[@id="SSUser_Logon_0-item-USERNAME"]')$sendKeysToElement(list("myusername"))
remDr$findElement('xpath', '//*[@id="SSUser_Logon_0-item-PASSWORD"]')$sendKeysToElement(list("password"))

remDr$findElement('xpath', '//*[@id="SSUser_Logon_0-button-Logon"]/span')$clickElement()

# Check if I slect element I want to click
webElem <- remDr$findElement('xpath', '//*[@id="climbingRoutes_next"]')
webElem$getElementAttribute("class")

# Extract html with Selenium + rvest
html <- read_html(remDr$getPageSource()[[1]])

# When having trouble "clicking", there are 3 options I am aware of (https://stackoverflow.com/questions/26725406/rselenium-radio-button-click-doesnt-seem-to-be-working)
webElem$clickElement()
webElem$sendKeysToElement(list(key="enter"))
remDr$executeScript("document.getElementById('#climbingRoutes_next').click()")
```

```{r}
# Try to use a while statement ...
url <- "https://www.kletterzentrum-innsbruck.at/index.php?id=235&no_cache=1"
  remDr$navigate(url)
  Sys.sleep(3)
  if(length(remDr$findElement('xpath', '//*[@id="climbingRoutes_next"]'))!=0){
    while(remDr$findElement('xpath', '//*[@id="climbingRoutes_next"]')$isElementDisplayed()[[1]]){
      tryCatch({
      Sys.sleep(1)
      webElem <- remDr$findElement('xpath', '//*[@id="climbingRoutes_next"]')
      webElem$sendKeysToElement(list(key="enter"))
      }, error=function(e){})
    }
  }
  mb<- read_html(remDr$getPageSource()[[1]])
```